\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Add dots to bibitems.
Add ZFS section.

\subsection{ZFS}
TODO

@@

\begin{thebibliography}{9}
\bibitem{BTRFS}
	Ohad Rodeh, Josef Bacik and Chris Mason.
	\textit{BTRFS: The Linux B-tree Filesystem}
	\\\texttt{https://domino.research.ibm.com/library/cyberdig.nsf\\/papers/6E1C5B6A1B6EDD9885257A38006B6130/\$File/rj10501.pdf}
	\\IBM Research, Fusion-IO.
\bibitem{rodeh}
	Ohad Rodeh.
	\textit{B-trees, shadowing, and clones}
	\\\texttt{\href{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}}
	USENIX Linux Storage \& Filesystem Workshop 2007. Also Rodeh, Ohad (2008). "B-trees, shadowing, and clones". ACM Transactions on Storage.
\bibitem{maid}
	Wikipedia.
	\textit{Evil Maid Attack}
	\\\texttt{\href{https://en.wikipedia.org/wiki/Evil\_maid\_attack}{https://en.wikipedia.org/wiki/Evil\_maid\_attack}}
\bibitem{IMA}
	Linux IMA Project
	\textit{IMA - Integrity Measurement Atchitecture}
	\\\texttt{\href{http://linux-ima.sourceforge.net/}{http://linux-ima.sourceforge.net/}}
\bibitem{HMAC}
	H. Krawczyk, M. Bellare, R. Canetti
	\textit{HMAC: Keyed-Hashing for Message Authentication}
	\\\texttt{\href{https://tools.ietf.org/html/rfc2104}{https://tools.ietf.org/html/rfc2104}}
	Request for Comments: 2104 	
\bibitem{FS-VERITY}
	J. Corbet
	\textit{Protecting files with fs-verity}
	\\\texttt{\href{https://lwn.net/Articles/763729/}{https://lwn.net/Articles/763729/}}
\bibitem{UBIFS}
	S. Hauer.
	\textit{UBIFS Authentication}
	\\\texttt{\href{https://www.kernel.org/doc/Documentation/filesystems/ubifs-authentication.md}{https://www.kernel.org/doc/Documentation/filesystems/ubifs-authentication.md}}
\end{thebibliography}
\end{document}

>>>>

\subsection{ZFS}
ZFS\cite{ZFS} is a File System originally developed at Sun Microsystems (now
Oracle) for the Solaris Operating System. ZFS uses a Merkle Tree\cite{ZFS} on
the block level with either the Fletcher2 or SHA-256 Hash algorithm. This
Merkle Tree is embedded into the File System's internal structure and in a
way that the File System's Superblock (or Uberblock in ZFS Terms) constantly
provides an up-to-date signature of the blocks in the File System.

@@

\begin{thebibliography}{9}
\bibitem{BTRFS}
	Ohad Rodeh, Josef Bacik and Chris Mason.
	\textit{BTRFS: The Linux B-tree Filesystem}
	\\\texttt{https://domino.research.ibm.com/library/cyberdig.nsf\\/papers/6E1C5B6A1B6EDD9885257A38006B6130/\$File/rj10501.pdf}
	\\IBM Research, Fusion-IO.
\bibitem{rodeh}
	Ohad Rodeh.
	\textit{B-trees, shadowing, and clones}
	\\\texttt{\href{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}}
	USENIX Linux Storage \& Filesystem Workshop 2007. Also Rodeh, Ohad (2008). "B-trees, shadowing, and clones". ACM Transactions on Storage.
\bibitem{maid}
	Wikipedia.
	\textit{Evil Maid Attack}
	\\\texttt{\href{https://en.wikipedia.org/wiki/Evil\_maid\_attack}{https://en.wikipedia.org/wiki/Evil\_maid\_attack}}
\bibitem{IMA}
	Linux IMA Project.
	\textit{IMA - Integrity Measurement Atchitecture}
	\\\texttt{\href{http://linux-ima.sourceforge.net/}{http://linux-ima.sourceforge.net/}}
\bibitem{HMAC}
	H. Krawczyk, M. Bellare, R. Canetti
	\textit{HMAC: Keyed-Hashing for Message Authentication}
	\\\texttt{\href{https://tools.ietf.org/html/rfc2104}{https://tools.ietf.org/html/rfc2104}}
	Request for Comments: 2104 	
\bibitem{FS-VERITY}
	J. Corbet.
	\textit{Protecting files with fs-verity}
	\\\texttt{\href{https://lwn.net/Articles/763729/}{https://lwn.net/Articles/763729/}}
\bibitem{UBIFS}
	S. Hauer.
	\textit{UBIFS Authentication}
	\\\texttt{\href{https://www.kernel.org/doc/Documentation/filesystems/ubifs-authentication.md}{https://www.kernel.org/doc/Documentation/filesystems/ubifs-authentication.md}}
\bibitem{ZFS}
	Oracle Corporation.
	\textit{ZFS End-to-End Data Integrity}
	\\\texttt{\href{https://blogs.oracle.com/bonwick/zfs-end-to-end-data-integrity}{https://blogs.oracle.com/bonwick/zfs-end-to-end-data-integrity}}
\end{thebibliography}
\end{document}
